Late Pleistocene stone artefact technology at Mau A, Yen Bai, Northern Vietnam

### 2022-03-18 analysis/paper/paper.Rmd
Slight edit to code creating the contribution bar plots to change the labels "A" and "B" to First and Second Princiap Components respectively. This commit also includes a rewrite of the portion of the discussion section describing the contribution plots; the previous text was inaccurate and based off of incorrect labels.

temp <- plot_grid(PC1_contrib +
             theme(axis.text = element_text(size = 5)),
          PC2_contrib + 
             theme(axis.text = element_text(size = 5)),
          labels = "AUTO"
  )

@@

Looking at \@ref(fig:contribution-plots), the landmarks which contributed the most to each principal component were all located on the left side of our artefacts. This means that linking our initial flake measurements (maximum length, top width etc.) to either of the first two principal components is nearly impossible, as every one of our initial flake measurements (with the) one can see that there is no consistent pattern in which certain initial flake measurements  align closely with either the first or second principal components. Interestingly, the landmarks which contributed the most to each principal component were all located on the left side of our artefacts..

>>>>

plot_grid(PC1_contrib +
             theme(axis.text = element_text(size = 5)),
          PC2_contrib + 
             theme(axis.text = element_text(size = 5)),
          labels = c("First Principal Component",
                     "Second Principal Component"),
          label_size = 6,
          hjust = -0.3)

@@

Looking at \@ref(fig:contribution-plots), we can see that certain landmarks contributed to each principal component. For the first principal component, the distal tip, the top right, and the top left landmarks are the top three contributors. We interpret this as indicating that the first principal component is primarily influenced by artefact length and platform breadth. The second principal component primarily consists of the bottom left, bottom right, top left, and top right landmarks; one can interpret this as the second principal component taking after overall width.
